Enhancement of SDR in Thessaloniki

### 2024-09-06 GHI_enh_03_process.tex
Commit 2024-09-06 14:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-05}

@@

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-72.8133 -27.4706   0.7672   0.4338  28.2495  83.4876 
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-333.34 -132.29  -52.26   96.74  664.64

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)    
(Intercept)      7.113e+00  4.604e+01   0.155    0.877    
as.numeric(Date) 2.252e-07  3.656e-08   6.160 1.98e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 189.5 on 354 degrees of freedom
Multiple R-squared:  0.09681,   Adjusted R-squared:  0.09426 
F-statistic: 37.94 on 1 and 354 DF,  p-value: 1.979e-09
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-333.34 -132.29  -52.26   96.74  664.64

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)       7.113e+00  4.604e+01   0.155    0.877    
ST_E_monthly$Date 2.252e-07  3.656e-08   6.160 1.98e-09 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 189.5 on 354 degrees of freedom
Multiple R-squared:  0.09681,   Adjusted R-squared:  0.09426 
F-statistic: 37.94 on 1 and 354 DF,  p-value: 1.979e-09
\end{verbatim}

@@

\begin{verbatim}
2024-09-05 19:30:15.8 athan@sagan GHI_enh_03_process.R 3.894151 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-06}

@@

\begin{verbatim}
    Min.  1st Qu.   Median     Mean  3rd Qu.     Max. 
-72.8133 -27.4706   0.7675   0.4342  28.2501  83.4876 
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-440.00 -199.37  -79.04  137.06  963.22

Coefficients:
                  Estimate Std. Error t value Pr(>|t|)    
(Intercept)      3.300e+01  6.644e+01   0.497     0.62    
as.numeric(Date) 2.926e-07  5.276e-08   5.546 5.73e-08 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 273.5 on 354 degrees of freedom
Multiple R-squared:  0.07994,   Adjusted R-squared:  0.07734 
F-statistic: 30.76 on 1 and 354 DF,  p-value: 5.728e-08
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-440.00 -199.37  -79.04  137.06  963.22

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)       3.300e+01  6.644e+01   0.497     0.62    
ST_E_monthly$Date 2.926e-07  5.276e-08   5.546 5.73e-08 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 273.5 on 354 degrees of freedom
Multiple R-squared:  0.07994,   Adjusted R-squared:  0.07734 
F-statistic: 30.76 on 1 and 354 DF,  p-value: 5.728e-08
\end{verbatim}

@@

\begin{verbatim}
2024-09-06 10:16:28.4 athan@sagan GHI_enh_03_process.R 3.892410 mins
\end{verbatim}

### 2024-09-06 GHI_enh_04_investigate.tex
Commit 2024-09-05 13:11
Commit 2024-09-06 00:14
Commit 2024-09-06 14:14

\begin{verbatim}
Warning: Removed 32 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 220 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 26591 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 220 rows containing non-finite outside the scale range (`stat_bin()`).
Removed 26591 rows containing non-finite outside the scale range (`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 14 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

lmY: 226.3963 +/- 31.30176

@@

lmY: 85.26719 +/- 10.01748

@@

lmY: 0.116043 +/- 0.055572

@@

lmY: 0.107931 +/- 0.044598

@@

lmY: 222.2785 +/- 28.96957

@@

lmY: 83.81382 +/- 9.456821

@@

lmY: 229.8063 +/- 39.56838

@@

lmY: 86.21667 +/- 12.87325

@@

lmY: 0.085425 +/- 0.09766

@@

lmY: 0.086495 +/- 0.070955

@@

\begin{verbatim}
2024-09-05 08:56:04.2 athan@sagan GHI_enh_04_investigate.R 13.014418 mins
\end{verbatim}

>>>>

\begin{verbatim}
Warning: Removed 29 rows containing missing values or values outside the scale
range (`geom_bar()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 364 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

\begin{verbatim}
Warning: Removed 34442 rows containing non-finite outside the scale range
(`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 364 rows containing non-finite outside the scale range (`stat_bin()`).
Removed 34442 rows containing non-finite outside the scale range (`stat_bin()`).
\end{verbatim}

@@

\begin{verbatim}
Warning: Removed 19 rows containing non-finite outside the scale range
(`stat_bin2d()`).
\end{verbatim}

@@

lmY: 325.2046 +/- 44.00396

@@

lmY: 110.9722 +/- 13.43944

@@

lmY: 0.14418 +/- 0.052969

@@

lmY: 0.125986 +/- 0.041509

@@

lmY: 320.1081 +/- 40.93156

@@

lmY: 109.4004 +/- 12.63018

@@

lmY: 329.8573 +/- 56.0224

@@

lmY: 112.1073 +/- 17.43077

@@

lmY: 0.111567 +/- 0.096855

@@

lmY: 0.10318 +/- 0.067313

@@

\begin{verbatim}
2024-09-06 10:26:49.9 athan@sagan GHI_enh_04_investigate.R 10.084896 mins
\end{verbatim}

### 2024-09-06 GHI_enh_08_validation.tex
Commit 2024-09-06 14:14

\caption{ - empty caption - }\label{fig:example-days-6}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-7}

\caption{ - empty caption - }\label{fig:example-days-7}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-8}

\caption{ - empty caption - }\label{fig:example-days-8}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-9}

\caption{ - empty caption - }\label{fig:example-days-9}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-10}

\caption{ - empty caption - }\label{fig:example-days-10}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-1}

\caption{ - empty caption - }\label{fig:unnamed-chunk-5-1}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-2}

\caption{ - empty caption - }\label{fig:unnamed-chunk-5-2}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-3}

\caption{ - empty caption - }\label{fig:unnamed-chunk-5-3}
\end{figure}

\begin{verbatim}
[1] 0.9972485
\end{verbatim}

@@

@@

\begin{verbatim}
2024-09-06 09:06:13.6 athan@sagan GHI_enh_08_validation.R 2.489076 mins
\end{verbatim}

>>>>

\caption{ - empty caption - }\label{fig:unnamed-chunk-6}
\end{figure}

@@

\begin{verbatim}
Call:
lm(formula = KEEP[, wattGLB, Low_B.Low_W.glo])

Coefficients:
(Intercept)      wattGLB  
     18.357        1.038  
\end{verbatim}

\newpage

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-7-1}

\caption{ - empty caption - }\label{fig:unnamed-chunk-7}
\end{figure}

data:  KEEP$wattGLB and KEEP$Enhanc_C_4_ref
t = 7938, df = 345175, p-value < 2.2e-16
alternative hypothesis: true correlation is not equal to 0
95 percent confidence interval:
 0.9972540 0.9972904
sample estimates:
      cor 
0.9972722 
\end{verbatim}

\begin{verbatim}
Call:
lm(formula = KEEP[, wattGLB, Enhanc_C_4_ref])

Coefficients:
(Intercept)      wattGLB  
     43.323        1.036  
\end{verbatim}

@@

\begin{verbatim}
2024-09-06 10:32:08.3 athan@sagan GHI_enh_08_validation.R 1.913171 mins
\end{verbatim}
